### 2016-09-01 latex/paper.tex
Started FEA results table

\newpage
\section*{LIST OF TERMS}
A partial list of symbols is given below. Other symbols are defined in-place on not re-used.

@@

>>>>

\newpage
\section*{LIST OF TERMS}
A partial list of symbols is given below. Other symbols are defined in-place or not re-used.

@@

\newpage
\section*{FINITE-ELEMENT RESULTS}
For all the following wheels: $R=0.3$ m, $EI_{11}=EI_{22}=69.0$ N-m$^2$, $GJ=26.0$ N-m$^2$,

\begin{tabular}{c|c|c}
$n_s$ & Hub flange width [mm] & Hub flange diameter [mm]\\
\hline

\end{tabular}
